Article analysis

### 2017-10-03 Article analysis.Rmd
librarys

Before I run any parts of the analysis, I load all the packages I use in this file
```{r load libraries}
require(dplyr)
require(ggplot2)
```
First in excel, I deleted two rows of non-table data, i.e. title, and a note, and saved the file (S2_Table) as a CSV in the project directory. Then I read it into R and converted it to a table using dplyr
```{r readfile}
iso<-read.csv("S2_Table.csv")
iso<-tbl_df(iso_total)
head(iso_total)
```

>>>>

Before I run any parts of the analysis, I load all the packages I use in this file
```{r load libraries}
require(dplyr)
require(stringr)
require(ggplot2)
require(qwraps2)
```
First in excel, I deleted two rows of non-table data, i.e. title, and a note, and saved the file (S2_Table) as a CSV in the project directory. Then I read it into R and converted it to a table using dplyr
```{r readfile}
iso<-read.csv("S2_Table.csv")
iso<-tbl_df(iso_total)
head(iso_total)
```
